---
title: "Prediction Tunning"
author: "Gustavo Monteiro"
date: "November 2, 2018"
output:
  html_document:
    df_print: paged
    toc: yes
    toc_float: yes
  html_notebook:
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
---
```{r setup, include=FALSE}
library(caret)
library(tidyverse)
```

> The database that will be used in this study consists of data on the votes that candidates for the Federal Chamber of Deputies received in the years 2006 and 2010 (source: http://www.tse.jus.br), as well as information on campaigning, party, schooling, ... of them.

## Loading data.
```{r}
train <- read.csv("train.csv")
test <- read.csv("test.csv")
```

## Removing categoric variables.
```{r}
train <- train %>% select(-nome, -uf, -estado_civil, 
                          -partido, -ocupacao,-ano, 
                          -cargo,-grau,-sexo, 
                          -sequencial_candidato)
```

> for this we will compare 3 types of regression, ridge, lasso and knn, which will be executed follow.

## Ridge regression.
```{r}
set.seed(1)

fitControl <- trainControl(method = "repeatedcv", number = 10, repeats = 10)
lambdaGrid <- expand.grid(lambda = 10^seq(10, -2, length=100))

# modelo utilizando regressão ridge
model <- train(votos ~ ., 
               data = train,
               method = "ridge",
               trControl = fitControl,
               preProcess = c('scale', 'center'),
               tuneGrid = lambdaGrid,
               na.action = na.omit)
model
ggplot(model)
```

> Variable importance for ridge regression

```{r}
ggplot(varImp(model))
```

## Lasso regression.
```{r}
set.seed(1)
lambda <- expand.grid(fraction = seq(0.01, 10^-8, length=20))
model_lasso <- train(votos ~ ., 
                     data = train, 
                     method = "lasso", 
                     tuneGrid = lambda,
                     preProc = c("center", "scale"),
                     trControl = fitControl)
ggplot(model_lasso)
model_lasso
```

> Variable importance for ridge regression

```{r}
ggplot(varImp(model_lasso))
```


## Knn regression.
```{r}
k <- expand.grid(k = seq(25, 50, length=81))
model_knn <- train(votos ~ ., 
                     data = train, 
                     method = "knn", 
                     tuneGrid = k,
                     preProc = c("center", "scale"),
                     trControl = fitControl)
ggplot(model_knn)
```

> Variable importance for ridge regression

```{r}
ggplot(varImp(model_knn))
```

## Results

For the tests done, we see that in all models the definition of which predictors are most useful basically does not change, what was expected, having only some eventual change of position in the ranking, but in all defining the most significant variables as `total_receita`, `total_despeza`, `resources_of_personal_juridicas`.

In terms of comparison of the forms of model creation, using as a parameter of comparison the [RMSE] (https://en.wikipedia.org/wiki/Root-mean-square_deviation), through the results we can see a better performance of the model created with knn, with a k defined at 32 bringing the best result, bringing an RMSE value close to 30100, while the lasso regression had its best result around 38,5K and the ridge around 38K.

Following a model using knn will be created, which proved to be the one with the best results and using only the best predictors, this prediction model will be used for prediction of votes over the 2014 elections data in Brazil

```{r}
model_knn_topper <- train(votos ~ total_receita * total_despesa * recursos_de_pessoas_juridicas, 
                     data = train, 
                     method = "knn", 
                     tuneGrid = k,
                     preProc = c("center", "scale"),
                     trControl = fitControl)
```

## Generation predictions for test dataframe to submit to Kaggle, to related [competition](https://www.kaggle.com/c/ufcg-cdp-20182).

NOTE: for a delay in sending, the following prediction does not appear in the ranking, but reached a score of 30888.82009, which would fit as the third place in the public ranking had it been sent on time.
```{r}
prediction <- predict(model_knn_topper, test)  
data_out <- data.frame(ID = test$sequencial_candidato, votos = prediction) 
data_out$ID <-as.character(data_out$ID)  
data_out %>% write_csv(path = "response.csv") 
prediction
```
